---
title: "My summer R coding notes"
author: "rp"
date: "8/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## How to make a new vignette

Get started with the package `usethis` and the function `use_vignette`:

```{r }
library(usethis)
usethis::use_vignette("report")
```

To render the vignette to pdf, you'll need  `rmarkdown` and run from R:

```{r}
# install the package first if necessary
# install.packages("rmarkdown")
rmarkdown::render("vignettes/report.Rmd", output_format="pdf_document")
```

##
The following function displays packages that are loaded in the R environment.

```{r, eval = TRUE}
my_packages <- library()$results[,1]
head(my_packages, 10)
```
```{r, eval = TRUE}
my_packages
```


To install `phyloch` we will use the package `devtools`.
```{r}
install.packages("devtools")
```

Then we can install `phyloch` from Github.
```{r}
devtools::install_github("fmichonneau/phyloch")
#ERROR: lazy loading failed for package 'phyloch'
#* removing 'C:/Users/randy/OneDrive/Documents/R/win-library/4.0/phyloch'
```

## Build my R package into a website

We will use an R package called `pkgdown` for this.

We took the following instructions from  https://pkgdown.r-lib.org/:

Get started with `use_pkgdown`. Run it once to configure your package to use `pkgdown`

```{r }
usethis::use_pkgdown()
```

Use `build_site` to update your website:

```{r}

# Run to build the website
pkgdown::build_site()
```

Now, your website will be built in the `docs` folder. Make sure that the folder is not in `.gitignore`.
Otherwise, it will not be uplodaded to GitHub and the website will not be available publicly!
